### 2012-12-17 annualreports/2012/balancesheet.tex
2012 annual report

\section{Balance Sheet}
31\superscript{st} March 2011

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2011} &  \multicolumn{2}{c}{2010} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                                & £      & £     & £     & £     \\
{\bf Fixed Assets}                              &        &       &       &       \\
{\bf Tangible fixed assets}                     &        & 5,525 &       & 1,040 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                            &        &       &       &       \\
Rental Deposit                                  & 7,696  &       &       &       \\
Cash at bank and in hand                        & 7,688  &       & 8,642 &       \\
Creditors: amounts falling due within one year  & -2,511 &       & -1,343&      \\
Prepaid Subscriptions                           & -610   &       &       &      \\
{\bf Net current assets}                        &        & 12,263 &       & 7,299 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}     &        & 17,787 &       & 8,339 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                  &        & 17,787 &       & 8,339 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on the 22\superscript{nd} of January 2012
\vspace{48pt}

>>>>

\section{Balance Sheet}
31\superscript{st} March 2012

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2012} &  \multicolumn{2}{c}{2011} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                               & £        & £       & £      & £      \\
{\bf Fixed Assets}                             &          &         &        &        \\
{\bf Tangible fixed assets}                    &          & 5,149   &        & 5,525  \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                           &          &         &        &        \\
Rental Deposit                                 & 7,696    &         & 7,696  &        \\
Inventory                                      & 163      &         & 0      &        \\
Cash at bank and in hand                       & 14,889   &         & 7,688  &        \\
Creditors: amounts falling due within one year & -167     &         & -2,511 &       \\
Prepaid Subscriptions                          & 0        &         & -610   &       \\
{\bf Net current assets}                       &          & 27,898  &        & 12,263 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}    &          & 27,732  &        & 17,787 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                 &          & 27,732  &        & 17,787 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on TBC
\vspace{48pt}

### 2012-12-17 annualreports/2012/directorsreport.tex
2012 annual report

\subsection{Objects of the Company}

The stated Objects of the Hackspace Foundation are:

\begin{itemize}
    \item To promote and support science, engineering, and art.
\end{itemize}

@@

The Hackspace Foundation is a Company Limited by Guarantee operating as a membership association.
The company has a Board of up to eight Directors who are elected by the membership and serve for a three-year term,
although this is mainly a symbolic role with most decisions made by membership consensus.

As the Foundation has grown since its formation in February 2009, it has historically not been possible
to reliably determine if it is eligible for charitable status. Combined with the administrative overhead of doing so,
this has so far prevented the Hackspace Foundation from becoming a registered charity.

Since the company is becoming more mature, it is becoming more clear that it is likely to be eligible for charitable status,
and we anticipate looking into applying within the next year.

@@

At the beginning of the 2010/2011 year, the London Hackspace was based in an 800 sq ft, unheated space in Barnsbury.
In July 2010 we moved to a 1300 sq ft space in Cremer Street, E2, and on January 1\(^{st}\) 2011 the space was expanded into
the adjacent unit to increase our space to 2600 sq ft.

Currently our space comprises desk space across two separate rooms, sofas, a kitchen, and a sizeable workshop with woodworking,
metalworking and other fabrication facilities.

Recent equipment purchases include a laser cutter for cutting and etching wood and plastic, and large lathe/mill for metalworking.
All this equipment is available for members to use for free or with a small contribution to equipment running costs.

@@

The Hackspace Foundation is a membership association, and membership is open to everyone.
Members receive 24-hour access to the space, storage space, and voting rights in return for a membership subscription.

The minimum membership subscription is £5 per month, and members are encouraged to pay what they consider their
membership to be worth.

Membership subscriptions are the primary source of income for the Hackspace Foundation, and in 2010/11 our
membership rapidly grew by 600\% from 41 to 252 people.

\subsection{Services for Non-Members}

Although we encourage anyone who finds the London Hackspace useful to become a member, we don't limit our services to members.
Non-members can use our facilities under the supervision of a member, and we run events (both free and paid) which are open to non-members.

There are many individual events organised by members on a regular basis, which are usually free and open to the public. Regular events include:

\begin{itemize}
    \item Weekly Meetups - our weekly public social events.
    \item DIY Bio - workshops and lectures on biology.
    \item Young Hackspace - free events for children aged between 6 and 10.
\end{itemize}

We also allow other like-minded non-profit groups to hire out sections of our space at cost - generally much cheaper than other similar venues.

\subsection{Public Benefit}

The London Hackspace is not currently a registered charity (see the Organisational Structure section on page \pageref{ref_structure} for more details),
which would require it to publish details of the public benefit it delivers. Nonetheless, the Directors feel it is appropriate to do so.

We believe the London Hackspace delivers charitable benefits under two of the headings allowed by the Charities Act 2006:
firstly and primarily through the advancement of the arts, culture, heritage or science, and secondly through the advancement of education.

As entry to the London Hackspace is free of charge for non-members, and the minimum membership is a modest fee, we
believe there are no unreasonable restrictions on access to the benefits which are therefore available to the public in accordance with the
definition of the Act.

@@

The Hackspace Foundation aims to keep three months worth of monthly running costs as a reserve. This currently amounts to £12,486.

Due to the significant membership growth of the London Hackspace during 2010/11, it was decided to spend some of the reserve on expanding the space.
The majority of this was spent on lease deposits. At the end of the financial year, our balance was £7,568.

@@

Approved by the Board for issue on the 28\superscript{th} of December 2011
\vspace{48pt}

>>>>

\subsection{Objects of the Association}

The stated Objects of London Hackspace are:

\begin{itemize}
    \item to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
    \item to provide and maintain shared community workspace and equipment in Greater London.
\end{itemize}

@@

The London Hackspace is a Company Limited by Guarantee operating as a membership association.
The company has a Board of up to nine Directors (known commonly as "Trustees") who are elected yearly by the membership and serve for a three-year term.
The role of the Trustees is primarily to provide overall guidance; day-to-day management of the facilities is handled by members on a volunteer basis.

\subsection{Charitable Status}

In our previous Annual Report, we raised the possibility of applying for charitable status.
After discussion with the Charity Commission during 2011, we concluded that this would not be
an appropriate route for London Hackspace to go down at this time.

@@

TBC

@@

TBC

@@

London Hackspace aims to keep three months worth of monthly running costs as a reserve.

@@

Approved by the Board for issue on TBC
\vspace{48pt}

### 2012-12-17 annualreports/2012/notes.tex
2012 annual report

\section {Notes to the Financial Statements}
\begin{enumerate}
    \item {\bf Accounting policies}
    \begin{enumerate}
        \item {\bf Accounting convention} \\
                The financial statements are prepared under the 
            historical cost convention and in accordance with the Financial Reporting 
            Standard for Smaller Entities (effective April 2008).
        \item {\bf Compliance with accounting standards} \\
            The financial statements are prepared in accordance with applicable United
            Kingdom Accounting Standards (United Kingdom Generally Accepted Accounting
            Practice), which have been applied consistently throughout the period.
        \item {\bf Turnover} \\
            Turnover represents amounts receivable for services.
        \item {\bf Tangible fixed assets and depreciation} \\
            Tangible fixed assets are stated at cost less depreciation. Depreciation is
            provided at rates calculated to write off the cost less estimated residual
            value of each asset over its expected useful life, as follows: \\[6pt]
            \begin{tabular}{  l  p{6.5cm} }
                \toprule
                Fixtures \& Fittings & Over 5 years at 20\% per annum on a straight line basis \\
                Plant \& Machinery & Over 4 years at 25\% per annum on a straight line basis \\
                \bottomrule
            \end{tabular}
    \end{enumerate}
    \item {\bf Change of depreciation policy} \label{depreciation_change} \\ 
        The directors have chosen to alter the depreciation policy to be more in line
        with the expected useful life of equipment, fixtures, and fittings, based on
        observations made in the last year. Fixtures and Fittings are now depreciated
        over five years, and plant and machinery over four years on a straight-line
        basis.

        For the 2010/11 reporting period, these changes have resulted in the
        depreciation charge being reduced from £1,325 to £952, which represents a 4\%
        increase of the operating surplus.

        The depreciation expenditure for the 2009-2010 financial year has been restated
        according to the new depreciation policy. This has resulted in a change of £13
        to the depreciation line, or less than 1\% of the surplus for that year.

\end{enumerate}

>>>>

\section {Notes to the Financial Statements}
\begin{enumerate}
    \item {\bf Accounting policies}
    \begin{enumerate}
        \item {\bf Accounting convention} \\
                The financial statements are prepared under the 
            historical cost convention and in accordance with the Financial Reporting 
            Standard for Smaller Entities (effective April 2008).
        \item {\bf Compliance with accounting standards} \\
            The financial statements are prepared in accordance with applicable United
            Kingdom Accounting Standards (United Kingdom Generally Accepted Accounting
            Practice), which have been applied consistently throughout the period.
        \item {\bf Turnover} \\
            Turnover represents amounts receivable for services.
        \item {\bf Tangible fixed assets and depreciation} \\
            Tangible fixed assets are stated at cost less depreciation. Depreciation is
            provided at rates calculated to write off the cost less estimated residual
            value of each asset over its expected useful life, as follows: \\[6pt]
            \begin{tabular}{  l  p{6.5cm} }
                \toprule
                Fixtures \& Fittings & Over 5 years at 20\% per annum on a straight line basis \\
                Plant \& Machinery & Over 4 years at 25\% per annum on a straight line basis \\
                \bottomrule
            \end{tabular}
    \end{enumerate}
\end{enumerate}
